---
title: University of the Philippines - Los Baños 1st Semester Enrolment for School
  Year 2018-2019
author: "Alexander N. Villasoto"
date: "5 December 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

- The [University of the Philippines Los Baños (UPLB)](http://uplb.edu.ph/), a coeducational publicly funded academic, research and extension institution, is one of the eight constituent universities of the University of the Philippines System.
- As a supporter of [Open Data Initiative in the Philippines](https://data.gov.ph/about), UPLB opened a dataset that summarizes their graduate school's enrolment data for the school year 2018-2019.
- The dataset is recently uploaded on Thursday, November 8, 2018 - 14:28. You can find more information [here](https://data.gov.ph/dataset/graduate-school-dataset).

## Goals

- The goal of this project is to create an interactive plot that shows the number of enrolees per program based on the preselected filters such as college (e.g. College_of_Agriculture_and_Food_Science) and degree (e.g. Master_of_Science). 
- The project is created using a combination of Shiny and Plotly. Codebase and documentation can be found [here](https://github.com/ArseniusNott/UPLB_Enrolment).

***

```{r knitr_plot, echo = FALSE}
knitr::include_app("https://arsenius.shinyapps.io/UPLB_First_Semester_Enrolment_for_SY_2018_2019/", height = "600px")
```
**It takes a while to load the bar plot. Please wait.**

## Additional Notes

The plot is uploaded via shinyapps.io, a free tier offering 24 hour usage limit per month. If you have problems viewing the plot, it might be that it reached the usage limit. If that is the case, you can email the author here [anvillasoto@gmail.com](mailto:anvillasoto@gmail.com). Thank you.

***